Luminance constancy under fixed geometry

### 2018-05-27 Draft5/draft5.tex
johannes is thru the captions

% Figure 1: Introduction
\begin{figure}
\centering
\begin{subfigure}{0.4 \textwidth}
	\centering
	\caption{}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure1/Figure1_a.png}
        \label{fig:introSchematic}
    \end{subfigure}
    \begin{subfigure}{0.55 \textwidth}   
        \caption{}    
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure1/Figure1_b.pdf}
        \label{fig:introExampleFigure}
    \end{subfigure}
    \label{introFigure}
    \caption{{\bf Color and luminance constancy:} (a)  The light reflected from an object to the eye depends both on the surface reflectance of the object and on the illumination. 
Additionally, the reflected light also depends on geometric factors, such as the object's shape, pose, and position. 
The human visual system is able to account for variations in the reflected light due to object-extrinsic factors and produce a percept of object color that is relatively stable across such variations, an ability called color constancy. 
(b) Images of a sphere under a fixed illuminant.  
Down each column, the reflectance function of the sphere varies only by a scale factor; the shape of the reflectance spectrum is held fixed.  
The shape of the reflectance spectrum varies across each row.
Within each row, the light reflectance value (LRV) of the spheres is constant. 
The values on the left of each row provide the corresponding LRV. 
We cast the problem of computational luminance constancy to be that of estimating the LRV of a target object from the image, across variation in other scene factors. 
Specifically, we study variation in target object relative surface reflectance, variation in illumination spectrum, and variation in the surface reflectance of the other objects in the scene.}
 \end{figure}
 %% DHB: Add comment that resolution here (and maybe in some other figures) is higher than that used for AMA.
 %% DHB: Add axis labels to (b).

@@

% Figure 2
\begin{figure}
\centering
\begin{subfigure}[b]{0.22 \textwidth}
        \caption{Library }
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure2/Figure2_a.png}
        \label{fig:baseSceneLibrary}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.22 \textwidth}
        \caption{Mill}    
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure2/Figure2_b.png}
        \label{fig:baseSceneMill}
    \end{subfigure}    
    ~
    \begin{subfigure}[b]{0.22 \textwidth}
        \caption{Table-Chairs}    
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure2/Figure2_c.png}
        \label{fig:baseSceneTableChairs}
    \end{subfigure}
    \caption{{\bf Base scenes.} Each panel shows a rendering of one base scene without additional inserted objects.  The reflectance spectra of the distinct surfaces and the spectral power distributions of the light sources in each scene have been assigned randomly from models of naturally occurring spectra (see text).}\label{fig:baseScenes}.
\end{figure}
%% DHB: We need to say that each image in (a) was scaled and tone mapped individually to optimize the mapping into the available display gamut.

@@

% Figure 3
\begin{figure}
\centering
    \begin{subfigure}[b]{0.14 \textwidth}
        \caption{Big-ball}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure3/Figure3_a.png}
        \label{fig:libraryWithBigBall}
    \end{subfigure}
     ~ 
    \begin{subfigure}[b]{0.14 \textwidth}
        \caption{Xylophone}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure3/Figure3_b.png}
        \label{fig:libraryWithXylophone}
    \end{subfigure}
     ~ 
    \begin{subfigure}[b]{0.14 \textwidth}
        \caption{Barrel}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure3/Figure3_c.png}
        \label{fig:libraryWithBarrel}
         \end{subfigure}
    ~
	\begin{subfigure}[b]{0.14 \textwidth}
        \caption{Ring toy}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure3/Figure3_d.png}
        \label{fig:libraryWithRingToy}
    \end{subfigure}
        ~
    	\begin{subfigure}[b]{0.14 \textwidth}
        \caption{Bottle}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure3/Figure3_e.png}
        \label{fig:libraryWithChampagneBottle}
    \end{subfigure}
\caption{{\bf Library base scene with inserted objects.} The rendering package can be used to insert objects into base scenes. The panels show different objects inserted in the library base scene. The objects were inserted at a user defined location in the image. Then the rendering viewpoint was set so that the object is at the center of the rendered image. In these panels, the full rendered image has been cropped so that the inserted object is visually salient.}\label{fig:libraryWithTarget}
\end{figure}

@@

    \caption{{\bf Scene transformations.} The properties of a visual scene can broadly be classified into two groups: geometrical (a-b) and spectral (c-e). Our rendering package provides control over the properties illustrated by the columns of the figure. (a) Variation in inserted object positions. (b) Variation in object pose. (c) Variation in the surface reflectance of the target object. (d) Variation in the spectral power distributions of the light sources. (e) Variation in surface reflectance of the background objects.
\label{fig:VWCCTransformations}}
\end{figure}
%% DHB: These are too dark in a printout.  Let's review how they are scaled.  Need to make sure we can see an effect of changing the illumination, might want to hand pick the illuminants used here to illustrate the effect.

@@

% Figure 5: Conditions Studied
\begin{figure}
\centering
	\begin{subfigure}[b]{0.33 \textwidth}
		\caption{Condition 1}
%		\includegraphics[width=\textwidth]{../FiguresDraft5/Figure2/Figure2_a.png}
		\includegraphics[width=\textwidth]{../FiguresDraft5/Figure1/Figure1_b.pdf}
 		\label{fig:backgroundVarying}
	\end{subfigure}
	\begin{subfigure}[b]{0.33 \textwidth}
        \caption{Condition 2}	
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure5/Figure5_b.pdf}
        \label{fig:targetIlluminantVarying}
    \end{subfigure}
	\begin{subfigure}[b]{0.33 \textwidth}
	\caption{Condition 3}	
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure5/Figure5_c.pdf}        
        \label{fig:allSpectraVarying}
    \end{subfigure}    
    \caption{{\bf Dataset Conditions 1-3:} sRGB renderings of illustrative images from the datasets for Conditions 1, 2 and 3. The numbers on the left indicate the standard luminance level of the target object. 5 images are shown at each luminance level. We studied three types of spectral variations. (a) Condition 1: target object relative surface reflectance spectrum variable, light source spectra fixed, background object spectra fixed (same as Fig.~\ref{fig:introExampleFigure}).
(b) Condition 2: target object relative surface reflectance spectrum variable, light source spectra variable, background object spectra fixed, (c) Condition 3: target object relative surface reflectance spectrum variable, light source spectra variable, background object spectra variable. The spheres in each row of each panel have the same surface luminance, while the spheres in each column of each panel have the same relative surface reflectance.  Across the three panels, spheres in corresponding locations have the same surface reflectance. In all three panels, the overall lights source spectra scale factors (see \nameref{Methods}) were drawn from a uniform distribution on the range [0.5, 1.5]. This is smaller than the variation we studied, but allows us to show the variation within the dynamic range available for the figure. The sRGB values for all three panels were normalized using a common scale factor prior to gamma correction.} 
\label{fig:studiedCases}
\end{figure}

@@

% Figure 8: Methods
\begin{figure}
\centering
\begin{subfigure}[b]{0.25 \textwidth}
		\centering
        \caption{sRGB rendering of a 3D scene}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure9/Figure9_a.png}
        \label{fig:3DScene}
    \end{subfigure}
    ~ 
    \begin{subfigure}[b]{0.19 \textwidth}   
    \hspace{0.1 \textwidth}
        \caption{Cropped image}
        \vspace{1.5mm}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure9/Figure9_b.png}
        \label{fig:croppedImage}
    \end{subfigure}
    ~ 
    \begin{subfigure}[b]{0.19 \textwidth}
    \hspace{0.1 \textwidth}
        \caption{Retinal image}
        \vspace{1.5mm}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure9/Figure9_c.png}
        \label{fig:croppedImageWithMosaic}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.2 \textwidth}
        \caption{Normalized cone contrast}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure9/Figure9_d.png}
        \label{fig:coneContrast}
    \end{subfigure}
    \label{fig:sceneWithCroppedImage}
    \caption{{\bf Pipeline for generating labeled datasets:}  For the supervised learning approach employed in this work, labeled images are generated as follows: (a) A 3D virtual scene, containing a target object is created. The rendering viewpoint is selected so that the target object is in the center of the image. Spectra are assigned to the target object, illuminants, and other objects in the scene using the statistical models described in the text. A multispectral image of the scene is then rendered. (b) The central portion of the rendered image, which contains the target object, is cropped. (c) The retinal image corresponding to the rendered image is computed, and this is used in turn to compute the excitations (taken as the number of photopigment isomerizations) of the cone photoreceptors. The figure shows the a rendering of the retinal image after optical blurring, with the location and identity of the cones indicated by an overlay (L cones: red, M cones: green, S cones: blue).  (d) The cone excitations are interpolated to estimate the responses of all the three types of cone at each location (demosaicing). Finally, the demosaiced images are contrast normalized.}
\end{figure}

@@

%% Details on ISETBIO computations from Nicolas (TEXT IN CAPS IS FROM VIJAY)
%% Scene: 
%%- the default mean luminance was set to 200, but there is a key-value param that could have overriden this value. 
%%  I do not know if this were the case.
%%
%% % MEAN LUMINANCE = 0, NO SCALING
%
%%- The default FOV was 1 deg, but there is a key-value param that could have overriden this value.
%%  I do not know if this were the case.
%%
%% % HORIZONTAL FOV = 1
%%
%%- Distance default is 1 meter, but there is  a key-value param that could have overriden this value.
%%  I do not know if this were the case.
%%
%%% DISTANCE 1M
%%
%%Optics: 
%%- 3 mm pupil, 17 mm focal length, with a spectro-spatial OTF described in  
%%  (Marimont & Wandell (1994) J. Opt. Soc. Amer. A,  v. 11, p. 3113-3122), 
%%   which includes axial chromatic aberration. However, there is key-value param o skip the OTF. 
%%   Not sure if this was used.  It it was used, the optics was set to diffraction limited.
%%
%% % SKIP OTF OFF:  'skipOTF', false ...  
%%
%%Lens: 
%%- not sure if the optical density is from Wyszecki&Stiles or from Stockman-Sharpe. 
%%  The isetbio file commend only says it is from PTB. David do you know, or should I check
%%  the data?
%%
%%Cone Mosaic: 
%%- rectangular cone mosaic with 0.6:0.3:0.1 LMS densities
%%- FOV was a key-value param, so I do not know what was used.
%%- Also the mosaic was subsampled  according to a cone-stride param, with a default of 15 cones
%%but there is a key-value param that could have overriden this value. I do not know what that parameter value was.
%%
%% CONE STRIDE = 3 'coneStride', 3, ... 
%%
%%
%%- There is a key-value pair to also low-pass the optical image with default value to not do so.
%%  If that was user-overriden the OI was lowpass filtered using a Gaussian whose sigma was dependent on the cone-stride param.
%%
%% LOW PASS FILTER = MATCH CONE STRIDE : lowPassFilter = 'matchConeStride';      
%%
%%- IntegrationTime was not specified, so it was the default which is 5 msec.
%%  The cone isomerization maps were also demosaiced using linear interpolation.
%%- The default isomerization noise was set to none, but there is a key-value parameter
%%  that can override it. I do not know what the value of that was.
%%
%% ISOMERIZATION NOISE = FROZEN, 'isomerizationNoise', 'frozen'
%%
%%-  Finally, there is a key-value param named 'coneEfficiencyBasedReponseScaling', which by default is set to 'none'
%%   But if it was user-set to non 'none' the code scaled the responses to simulate equal quantal efficiencies 
%%   for L , M and S coneEfficiencyBasedReponseScaling by undoing filtering by the lens and the macular pigment.
%%   I do not know if this was used.
%% 
%% coneEfficiencyBasedReponseScaling = 'area'

@@

\section{Results} \label{Results}
%% Figure 10: Results for Condition 1
\begin{figure}
\centering
            \begin{subfigure}[b]{0.25 \textwidth}
        \caption{LRV estimates}
        \includegraphics[width=\textwidth, trim={0 0 0 1.3cm},clip]{../FiguresDraft5/Figure10/Figure10_a.pdf}
        \label{fig:case1Estimates}
    \end{subfigure} 
        \begin{subfigure}[b]{0.26 \textwidth}
        \caption{RF responses}
        \includegraphics[width=\textwidth, trim={0 3mm 0 15mm},clip]{../FiguresDraft5/Figure10/Figure10_b.pdf}
        \label{fig:case1RFResponse}
    \end{subfigure}
    \begin{subfigure}[b]{0.4 \textwidth}
	\caption{AMA receptive fields}
	\includegraphics[width=1.0\textwidth, trim={0.2cm -0.cm 0 0.3cm}]{../FiguresDraft5/Figure10/Figure10_c.pdf}
	\label{fig:case1RFs}
    \end{subfigure}   
    \caption{{\bf Condition 1 results:} (a) Mean estimated LRV $\pm$ 1 standard deviation for images in the test set obtained using linear regression and AMA estimators, based on the cone excitations. Solid lines show the mean estimate, the filled region in lighter color shows $\pm$ 1 standard deviation. The diagonal identity line (dotted blue) indicates veridical estimation. The standard deviations are too small to be visible. Relative RMSE (see Fig.\ref{fig:barGraphs}) is 0.8\% for linear regression and 1.1\%  for AMA based estimation. (b) Cone excitations projected along the first two AMA receptive fields for training images of Condition 1. Each cloud represents the image patches corresponding to one LRV. The clouds are approximated by a multivariate Gaussians whose means and variances are approximated by the ellipses shown in the figure. (c) The first two AMA receptive fields learnt using the cone excitations of stimuli in the training set.}
\label{fig:Condition1}
\end{figure}

@@

%% Figure condition 2: Excitations Fail
\begin{figure}
\centering
    \begin{subfigure}[b]{0.22\textwidth}   
        \caption{\centering{LRV estimates} \newline\centering{(Excitations)}}
        \includegraphics[width=\textwidth, trim={0 0 0 1.5cm},clip]{../FiguresDraft5/Figure11/Figure11_a.pdf}
        \label{fig:case2IsomerizationEstimates}
    \end{subfigure}
        \begin{subfigure}[b]{0.22 \textwidth}
        \caption{\centering{RF responses} \newline\centering{(Excitations)}}
        \includegraphics[width=\textwidth, trim={0 0 0 1.5cm},clip]{../FiguresDraft5/Figure11/Figure11_b.pdf}
        \label{fig:case2RFResponseIsomer}
    \end{subfigure}
            \begin{subfigure}[b]{0.22 \textwidth}
        \caption{\centering{LRV estimates}  \newline \centering{(Normalized contrast)}}
        \includegraphics[width=\textwidth, trim={0 0 0 1.5cm},clip]{../FiguresDraft5/Figure11/Figure11_c.pdf}
        \label{fig:case2ContrastEstimates}
    \end{subfigure}
            \begin{subfigure}[b]{0.22 \textwidth}
        \caption{\centering{RF responses}  \newline \centering{(Normalized contrast)}}
        \includegraphics[width=\textwidth, trim={0 0 0 1.5cm},clip]{../FiguresDraft5/Figure11/Figure11_d.pdf}
        \label{fig:case2RFResponseContrast}
    \end{subfigure}
    \caption{{\bf Condition 2 results:} (a) Mean estimated LRV $\pm$ 1 standard deviation for images in the test set obtained using linear regression and AMA estimators, based on the cone excitations. The relative RMSE is high (41.4\% for linear regression and 31.3\% for AMA based estimation). (b) Cone isomerizations projected on AMA receptive fields calculated using cone excitations. (c) Mean estimated LRV $\pm$ 1 standard deviation for images in the test set obtained using linear regression and AMA estimators, based on the contrast normalized cone excitations. The relative RMSE of estimation is 9.3\% for linear regression and 1.1\% for AMA based estimator. (d) The contrast normalized cone excitations projected along the first two AMA receptive fields. The receptive fields were learned using AMA and the contrast normalized cone excitations. For Condition 2, the response corresponding to individual image patches at each LRV level separates much better when the input is contrast normalized cone excitations rather than the cone excitations themselves.}
\label{fig:Condition2}
\end{figure}

@@

% Figure Error Bar Graphs
\begin{figure}
\centering
\includegraphics[width=0.6\textwidth]{../FiguresDraft5/FigureRMSEVsN/Figure14.pdf}
\caption{{\bf Variation of relative RMSE with number of RFs and size of training set:} (a) Variation of relative RMSE for Condition 3 as the size of training set. The relative RMSE converges around 2000 images. (b) Variation of relative RMSE v/s the number of receptive fields used in estimation. The performance converges around 6 Rfs}
 \label{fig:barGraphs}
\end{figure}
%% DHB: It might be natural here to show a plot of relative RMSE versus number of receptive fields, and for the best number of receptive
% fields of relative RMSE versus size of training set.  We want to persuade the reader that we are at asymptote.
% JDB: If we do this, it is probably best to put the evidence in the appendix. Otherwise, it will require a detour paragraph and figure subpanel.

>>>>

% Figure 1: Introduction
\begin{figure}
\centering
\begin{subfigure}{0.4 \textwidth}
	\centering
	\caption{}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure1/Figure1_a.png}
        \label{fig:introSchematic}
    \end{subfigure}
    \begin{subfigure}{0.55 \textwidth}   
        \caption{}    
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure1/Figure1_b.pdf}
        \label{fig:introExampleFigure}
    \end{subfigure}
    \label{introFigure}
    \caption{{\bf Color and luminance constancy:} (a)  The light reflected from an object to the eye depends both on the surface reflectance of the object and on the illumination of the object. 
The reflected light also depends on geometric factors, such as the object's shape, pose, and position. 
The human visual system accounts for variations in the reflected light due to object-extrinsic factors and produces a percept of object color that is relatively stable across such variations, an ability called color constancy. 
(b) Images of a sphere under a fixed illuminant.  
Down each column, the sphere's luminance reflectance value (LRV) varies, but the shape of the reflectance spectrum is held fixed.
Across each row, the shape of the reflectance spectrum varies, but the LRV is held fixed.
We cast the problem of computational luminance constancy to be that of estimating the LRV of a target object from the image, across variation in other scene factors. 
Specifically, we study variation in target object relative surface reflectance, variation in illumination spectrum, and variation in the surface reflectance of the other objects in the scene.}
 \end{figure}
 %% DHB: Add comment that resolution here (and maybe in some other figures) is higher than that used for AMA.
 %% DHB: Add axis labels to (b).

@@

% Figure 2
\begin{figure}
\centering
\begin{subfigure}[b]{0.22 \textwidth}
        \caption{Library }
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure2/Figure2_a.png}
        \label{fig:baseSceneLibrary}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.22 \textwidth}
        \caption{Mill}    
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure2/Figure2_b.png}
        \label{fig:baseSceneMill}
    \end{subfigure}    
    ~
    \begin{subfigure}[b]{0.22 \textwidth}
        \caption{Table-Chairs}    
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure2/Figure2_c.png}
        \label{fig:baseSceneTableChairs}
    \end{subfigure}
    \caption{{\bf Base scenes.} Each subplot shows a rendering of one base scene without additional inserted objects.  The reflectance spectra of the distinct surfaces and the spectral power distributions of the light sources in each scene have been assigned randomly from statistical models of naturally occurring spectra (see text).}\label{fig:baseScenes}.
\end{figure}
%% DHB: We need to say that each image in (a) was scaled and tone mapped individually to optimize the mapping into the available display gamut.

@@

% Figure 3
\begin{figure}
\centering
    \begin{subfigure}[b]{0.14 \textwidth}
        \caption{Big-ball}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure3/Figure3_a.png}
        \label{fig:libraryWithBigBall}
    \end{subfigure}
     ~ 
    \begin{subfigure}[b]{0.14 \textwidth}
        \caption{Xylophone}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure3/Figure3_b.png}
        \label{fig:libraryWithXylophone}
    \end{subfigure}
     ~ 
    \begin{subfigure}[b]{0.14 \textwidth}
        \caption{Barrel}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure3/Figure3_c.png}
        \label{fig:libraryWithBarrel}
         \end{subfigure}
    ~
	\begin{subfigure}[b]{0.14 \textwidth}
        \caption{Ring toy}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure3/Figure3_d.png}
        \label{fig:libraryWithRingToy}
    \end{subfigure}
        ~
    	\begin{subfigure}[b]{0.14 \textwidth}
        \caption{Bottle}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure3/Figure3_e.png}
        \label{fig:libraryWithChampagneBottle}
    \end{subfigure}
\caption{{\bf Library base scene with inserted objects.} The rendering package can be used to insert objects into base scenes. The subplots show different objects inserted in the library base scene at a user specified location. Then the rendering viewpoint was set so that the object was at the center of the rendered image. In these subplots, the full rendered image has been cropped so that the inserted object is takes up a large proportion of the presented image patch.}\label{fig:libraryWithTarget}
\end{figure}

@@

    \caption{{\bf Scene transformations.} The properties of a visual scene can be broadly classified into two groups: geometrical (a-b) and spectral (c-e). Our rendering package provides control over the properties illustrated by the columns of the figure. (a) Variation in inserted object positions. (b) Variation in object pose. (c) Variation in the surface reflectance of the target object. (d) Variation in the spectral power distributions of the light sources. (e) Variation in surface reflectance of the background objects.
\label{fig:VWCCTransformations}}
\end{figure}
%% DHB: These are too dark in a printout.  Let's review how they are scaled.  Need to make sure we can see an effect of changing the illumination, might want to hand pick the illuminants used here to illustrate the effect.

@@

% Figure 5: Conditions Studied
\begin{figure}
\centering
	\begin{subfigure}[b]{0.33 \textwidth}
		\caption{Condition 1}
%		\includegraphics[width=\textwidth]{../FiguresDraft5/Figure2/Figure2_a.png}
		\includegraphics[width=\textwidth]{../FiguresDraft5/Figure1/Figure1_b.pdf}
 		\label{fig:backgroundVarying}
	\end{subfigure}
	\begin{subfigure}[b]{0.33 \textwidth}
        \caption{Condition 2}	
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure5/Figure5_b.pdf}
        \label{fig:targetIlluminantVarying}
    \end{subfigure}
	\begin{subfigure}[b]{0.33 \textwidth}
	\caption{Condition 3}	
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure5/Figure5_c.pdf}        
        \label{fig:allSpectraVarying}
    \end{subfigure}    
    \caption{{\bf Dataset Conditions 1-3:} sRGB renderings of illustrative images from the datasets for Conditions 1, 2, and 3. Five images are shown for each luminance reflectance value (LRV). Each dataset had at least 100 images for each LRV. We studied three types of spectral variations. (a) Condition 1: variable target object relative surface reflectance spectrum, fixed light source spectra, fixed background object spectra (same as Fig.~\ref{fig:introExampleFigure}).
(b) Condition 2: variable target object relative surface reflectance spectrum, variable light source spectra, fixed background object spectra, (c) Condition 3: variable target object relative surface reflectance spectrum, variable light source spectra, variable background object spectra. The spheres in each row of subplots have the same LRV, while the spheres in each column of each subplot have the same relative surface reflectance.  Across the three sets of subplots, spheres in corresponding locations have the same surface reflectance. In all three subplots, the overall lights source spectra scale factors (see \nameref{Methods}) were drawn from a uniform distribution on the range [0.5, 1.5]. This is smaller than the variation we studied, but allows us to show the variation within the dynamic range available for computer monitors and printed figures. The sRGB values for all three subplots were normalized using a common scale factor prior to gamma correction.} 
\label{fig:studiedCases}
\end{figure}
%%JDB: ADD "Luminance Reflectance Value (LRV) label to the left-most y-axis.
%%JDB: DOUBLE CHECK FIRST SENTENCE ON SECOND LINE OF CAPTION: "Each dataset had at least 100 images for each LRV."
%% JDB: "relative surface reflectance" AFTER CONDITION 3 IS DESCRIBED... CHANGE TO WHATEVER OUR STANDARD TERM IS... "shape of reflectance spectra"?
%% JDB: I changed: "Across the subplots" to "Across the three sets of subplots"... DOUBLE CHECK THAT THE LANGUAGE IS CORRECT.
%% JDB: update range [0.5, 1.5] so it is anchored to a luminance level...
%% JDB: Changed "dynamic range available for computer monitors and printed figures" to "dynamic range available for computer monitors and printed figures".  OK WITH VIJAY AND DAVID?

@@

% Figure 8: Methods
\begin{figure}
\centering
\begin{subfigure}[b]{0.25 \textwidth}
		\centering
        \caption{sRGB rendering of a 3D scene}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure9/Figure9_a.png}
        \label{fig:3DScene}
    \end{subfigure}
    ~ 
    \begin{subfigure}[b]{0.19 \textwidth}   
    \hspace{0.1 \textwidth}
        \caption{Cropped image}
        \vspace{1.5mm}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure9/Figure9_b.png}
        \label{fig:croppedImage}
    \end{subfigure}
    ~ 
    \begin{subfigure}[b]{0.19 \textwidth}
    \hspace{0.1 \textwidth}
        \caption{Retinal image}
        \vspace{1.5mm}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure9/Figure9_c.png}
        \label{fig:croppedImageWithMosaic}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.2 \textwidth}
        \caption{Normalized cone contrast}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure9/Figure9_d.png}
        \label{fig:coneContrast}
    \end{subfigure}
    \label{fig:sceneWithCroppedImage}
    \caption{{\bf Pipeline for generating labeled datasets:}  The labeled images used in this paper are generated as follows: (a) A 3D virtual scene, containing a target object is created. The rendering viewpoint is selected so that the target object is in the center of the image. Spectra are assigned to the target object, illuminants, and other objects in the scene using the statistical models described in the text. A multispectral image of the scene is then rendered. (b) The central portion of the rendered image is cropped around the target object. (c) The retinal image corresponding to the rendered image is computed, which is then used to compute the number of photopigment isomerizations in the cone photoreceptors. The figure shows a rendering of the retinal image after optical blurring, with the location and identity of the cones indicated by an overlay (L cones: red, M cones: green, S cones: blue).  (d) The cone excitations are linearly interpolated to estimate the responses of all the three types of cone at each location (demosaicing). Finally, the demosaiced images are contrast normalized.}
\end{figure}

@@

%% Details on ISETBIO computations from Nicolas (TEXT IN CAPS IS FROM VIJAY)
%% Scene: 
%%- the default mean luminance was set to 200, but there is a key-value param that could have overridden this value. 
%%  I do not know if this were the case.
%%
%% % MEAN LUMINANCE = 0, NO SCALING
%
%%- The default FOV was 1 deg, but there is a key-value param that could have overridden this value.
%%  I do not know if this were the case.
%%
%% % HORIZONTAL FOV = 1
%%
%%- Distance default is 1 meter, but there is  a key-value param that could have overridden this value.
%%  I do not know if this were the case.
%%
%%% DISTANCE 1M
%%
%%Optics: 
%%- 3 mm pupil, 17 mm focal length, with a spectro-spatial OTF described in  
%%  (Marimont & Wandell (1994) J. Opt. Soc. Amer. A,  v. 11, p. 3113-3122), 
%%   which includes axial chromatic aberration. However, there is key-value param o skip the OTF. 
%%   Not sure if this was used.  It it was used, the optics was set to diffraction limited.
%%
%% % SKIP OTF OFF:  'skipOTF', false ...  
%%
%%Lens: 
%%- not sure if the optical density is from Wyszecki&Stiles or from Stockman-Sharpe. 
%%  The isetbio file commend only says it is from PTB. David do you know, or should I check
%%  the data?
%%
%%Cone Mosaic: 
%%- rectangular cone mosaic with 0.6:0.3:0.1 LMS densities
%%- FOV was a key-value param, so I do not know what was used.
%%- Also the mosaic was subsampled  according to a cone-stride param, with a default of 15 cones
%%but there is a key-value param that could have overridden this value. I do not know what that parameter value was.
%%
%% CONE STRIDE = 3 'coneStride', 3, ... 
%%
%%
%%- There is a key-value pair to also low-pass the optical image with default value to not do so.
%%  If that was user-overridden the OI was lowpass filtered using a Gaussian whose sigma was dependent on the cone-stride param.
%%
%% LOW PASS FILTER = MATCH CONE STRIDE : lowPassFilter = 'matchConeStride';      
%%
%%- IntegrationTime was not specified, so it was the default which is 5 msec.
%%  The cone isomerization maps were also demosaiced using linear interpolation.
%%- The default isomerization noise was set to none, but there is a key-value parameter
%%  that can override it. I do not know what the value of that was.
%%
%% ISOMERIZATION NOISE = FROZEN, 'isomerizationNoise', 'frozen'
%%
%%-  Finally, there is a key-value param named 'coneEfficiencyBasedReponseScaling', which by default is set to 'none'
%%   But if it was user-set to non 'none' the code scaled the responses to simulate equal quantal efficiencies 
%%   for L , M and S coneEfficiencyBasedReponseScaling by undoing filtering by the lens and the macular pigment.
%%   I do not know if this was used.
%% 
%% coneEfficiencyBasedReponseScaling = 'area'

@@

\section{Results} \label{Results}
%% Figure 10: Results for Condition 1
\begin{figure}
\centering
            \begin{subfigure}[b]{0.25 \textwidth}
        \caption{LRV estimates}
        \includegraphics[width=\textwidth, trim={0 0 0 1.3cm},clip]{../FiguresDraft5/Figure10/Figure10_a.pdf}
        \label{fig:case1Estimates}
    \end{subfigure} 
        \begin{subfigure}[b]{0.26 \textwidth}
        \caption{RF responses}
        \includegraphics[width=\textwidth, trim={0 3mm 0 15mm},clip]{../FiguresDraft5/Figure10/Figure10_b.pdf}
        \label{fig:case1RFResponse}
    \end{subfigure}
    \begin{subfigure}[b]{0.4 \textwidth}
	\caption{AMA receptive fields}
	\includegraphics[width=1.0\textwidth, trim={0.2cm -0.cm 0 0.3cm}]{../FiguresDraft5/Figure10/Figure10_c.pdf}
	\label{fig:case1RFs}
    \end{subfigure}   
    \caption{{\bf Condition 1 results:} (a) Mean estimated LRV $\pm$ 1 standard deviation for images in the test set obtained using the AMA-based estimator and linear regression on the cone excitations. Solid lines show the mean estimate, the filled region in lighter color shows $\pm$ 1 standard deviation. The diagonal identity line (dotted blue) indicates veridical estimation. The standard deviations are too small to be visible. Relative RMSE (see Fig.\ref{fig:barGraphs}) is 0.8\% for linear regression and 1.1\%  for AMA based estimation. (b) Training image cone excitations in Condition 1 projected onto the first two AMA receptive fields. Each cluster of responses represents the image patches associated with a particular LRV, which is coded by color. The response clusters are approximated by a multivariate Gaussians whose mean and covariance matrices are represented by the ellipses shown in the figure. (c) The first two AMA receptive fields learned using the cone excitations of stimuli in the training set.}
\label{fig:Condition1}
\end{figure}

@@

%% Figure condition 2: Excitations Fail
\begin{figure}
\centering
    \begin{subfigure}[b]{0.22\textwidth}   
        \caption{\centering{LRV estimates} \newline\centering{(Excitations)}}
        \includegraphics[width=\textwidth, trim={0 0 0 1.5cm},clip]{../FiguresDraft5/Figure11/Figure11_a.pdf}
        \label{fig:case2IsomerizationEstimates}
    \end{subfigure}
        \begin{subfigure}[b]{0.22 \textwidth}
        \caption{\centering{RF responses} \newline\centering{(Excitations)}}
        \includegraphics[width=\textwidth, trim={0 0 0 1.5cm},clip]{../FiguresDraft5/Figure11/Figure11_b.pdf}
        \label{fig:case2RFResponseIsomer}
    \end{subfigure}
            \begin{subfigure}[b]{0.22 \textwidth}
        \caption{\centering{LRV estimates}  \newline \centering{(Normalized contrast)}}
        \includegraphics[width=\textwidth, trim={0 0 0 1.5cm},clip]{../FiguresDraft5/Figure11/Figure11_c.pdf}
        \label{fig:case2ContrastEstimates}
    \end{subfigure}
            \begin{subfigure}[b]{0.22 \textwidth}
        \caption{\centering{RF responses}  \newline \centering{(Normalized contrast)}}
        \includegraphics[width=\textwidth, trim={0 0 0 1.5cm},clip]{../FiguresDraft5/Figure11/Figure11_d.pdf}
        \label{fig:case2RFResponseContrast}
    \end{subfigure}
    \caption{{\bf Condition 2 results:} (a) Mean estimated LRV $\pm$ 1 standard deviation for images in the test set obtained using the AMA-based estimator and linear regression from the cone excitations. The relative RMSE is high (41.4\% for linear regression and 31.3\% for AMA based estimation). (b) Cone excitations projected onto AMA receptive fields. (c) Mean estimated LRV $\pm$ 1 standard deviation for images in the test set obtained using the AMA-based estimator and linear regression from the contrast normalized cone excitations. The relative RMSE of estimation is 9.3\% for linear regression and 1.1\% for AMA based estimator. (d) The contrast normalized cone excitations projected along the first two AMA receptive fields. The receptive fields were learned using AMA and the contrast normalized cone excitations. For Condition 2, the response corresponding to individual image patches at each LRV level separates much better when the input is contrast normalized cone excitations than when the input is the raw cone excitations.}
\label{fig:Condition2}
\end{figure}

@@

% Figure Error Bar Graphs
\begin{figure}
\centering
\includegraphics[width=0.6\textwidth]{../FiguresDraft5/FigureRMSEVsN/Figure14.pdf}
\caption{{\bf Change of relative RMSE with number of receptive fields (RFs) and size of training set:} (a) Change of relative RMSE for Condition 3 with the size of training set. The relative RMSE converges around 2000 images. (b) Change of relative RMSE with the number of receptive fields. Performance converges around 6 RFs}
 \label{fig:barGraphs}
\end{figure}
%% DHB: It might be natural here to show a plot of relative RMSE versus number of receptive fields, and for the best number of receptive
% fields of relative RMSE versus size of training set.  We want to persuade the reader that we are at asymptote.
% JDB: If we do this, it is probably best to put the evidence in the appendix. Otherwise, it will require a detour paragraph and figure subpanel.
